\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-14 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates

The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}. The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}. In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate.

\medskip
Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics. In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced. The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeabilities. A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$. Viscosity ratio is set to 10.

>>>>

The dynamic mesh adaptive algorithm embedded in the Fluidity/IC-FERST model utilises a metric tensor field dependent on solution interpolation error-estimates which locally control the topology of elements in the metric \citep{pain_2001,power_2006}. Mesh optimisation generates unstructured finer mesh in regions where flow properties change faster and coarser mesh in regions where properties change more slowly \citep{piggott_2006}. The mesh adapts in three stages: metric formation, mesh optimisation and fields' interpolation from the pre- to post-adapted mesh \citep[see][]{hiester_2014}. In the simulations shown in this work, mesh will adapt as a response to oscillations in the phase saturation field with prescribed interpolation error estimate \citep{mostaghimi_2016}.

\medskip
Here, two numerical simulations were conducted with fixed and adaptive mesh resolutions to qualitatively assess model capability to capture fingers dynamics. In order to trigger the formation of fingers, regions with sharp synthetic permeability gradient were introduced. The computational space, Fig.~\ref{fig:testcase_heter_domain}a, consists of a rectangular domain fully saturated with a fluid (except by a squared region containing 50$\%$ of a second fluid -- wetting fluid phase, Fig.~\ref{fig:testcase_heter_domain}b) and divided into 5 regions with prescribed permeabilities. A no-flux boundary condition was imposed on upper and lower borders, whilst pure wetting fluid phase $\left(\text{\ie} S_{1}=1\right)$ is driven into the domain from the left-hand face at velocity $u_{1}=1$. Viscosity ratio of the two fluids is set to 10.
